RNeXML: a package for reading and writing richly annotated phylogenetic, character, and trait data in R

### 2015-05-29 manuscripts/manuscript.tex
committing submitted manuscript.tex file (automatically generated from .Rmd) and submit.tex (slightly modified by hand for ScholarOne compatibility)

This project was supported in part by the National Evolutionary
Synthesis Center (NESCent) (NSF \#EF-0905606), and grants from the
National Science Foundation (DBI-1306697) and the Alfred P Sloan
Foundation (Grant 2013-6-22). \texttt{RNeXML} started as a project idea
for the Google Summer of Code(TM), and we thank Kseniia Shumelchyk for
taking the first steps to implement it. We are grateful to F. Michonneau
for helpful comments on an earlier version of this manuscript.

@@

>>>>

This project was supported in part by the National Evolutionary
Synthesis Center (NESCent) (NSF \#EF-0905606), and grants from the
National Science Foundation (DBI-1306697) and the Alfred P Sloan
Foundation (Grant 2013-6-22). \texttt{RNeXML} started as a project idea
for the Google Summer of Code(TM), and we thank Kseniia Shumelchyk for
taking the first steps to implement it. We are grateful to F. Michonneau
for helpful comments on an earlier version of this manuscript, and
reviews by Matthew Pennell, Associate Editor Richard FitzJohn, and an
anonymous reviewer. At their behest, the reviews of FitzJohn and Pennell
can be found in this project's GitHub page at
\href{https://github.com/ropensci/RNeXML/issues/121}{github.com/ropensci/RNeXML/issues/120}
and
\href{https://github.com/ropensci/RNeXML/issues/120}{github.com/ropensci/RNeXML/issues/120},
together with our replies and a record of our revisions.

\subsection{Data Accessibility}\label{data-accessibility}

All software, scripts and data used in this paper can be found in the
permanent data archive Zenodo under the digital object identifier
\url{doi:10.5281/zenodo.13131} (Boettiger \emph{et al.} 2014). This DOI
corresponds to a snapshot of the GitHub repository at
\href{https://github.com/ropensci/RNeXML}{github.com/ropensci/RNeXML}.

@@

Boettiger, C., Vos, R., Chamberlain, S. \& Lapp, H. (2014). RNeXML
v2.0.0. Retrieved from \url{http://dx.doi.org/10.5281/zenodo.13131}
